Automatic Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-07 paper/paper_new.tex
Edited Sections 2 & 3.

\section{Related Work}
\subsection{Metadata for Natural History Image Collection}
%question/comment - we need to keep in mind we are deal with digitized specimens, not simply digital, in other words, the artifacts themselves are digital version of physical, not like an x-ray, where the image is digital from the start.  
A number of different metadata standards have been applied to support the description and access of digitized scientific images. The Darwin Core (DwC)~\cite{biodiv_info_standards}, developed specifically to describe biological diversity data is among the most popular standard for such efforts. It is an extension of the Dublin Core's DCMI Metadata Terms~\cite{dc_terms}. The Audubon Core~\cite{audub_core} supporting the discoverability, dissemination, and use of data relating to biological organisms, including 3--D digitized specimens, is an DwC extension that has become more popular. All of these descriptive standards and extensions include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the lens of a human curator. In other words, their application anticipates that a curator or data entry staff will manually generate metadata, drawing from acquisition logs or original specimen labels. This task is labor intensive, and the metadata associated with each digital rendering is generally sparse and more prone to human error, placing limitations on a researcher seeking to apply machine learning to the image and the metadata for scientific research.

This limitation is magnified when trying to assess the actual quality of the digitized specimen. Descriptive oriented standards support search and retrieval, and the biodiversity community has advocated for data fitness standards \cite{chapman2020developing}. This point is also emphasized by Wieczorek~\cite{wieczorek2012darwin} in their report on the variety of DwC metadata extensions to meet growing community concerns and needs, including data quality and fitness. Even so, metadata describing image quality is severely limited and generally missing. This point is addressed in detail in \cite{leipzig2021biodiversity}, serves as the rationale for Tulane University's effort to manually capturing content for 22 metadata properties characterizing digitized specimen image quality. Their work is being conducted in connection with the lager BGNN initiative, and the current process is costly in terms of labor and time, prone to human error and inconsistencies, and underscores the need to
explore automatic metadata generation methods.
%Fish species dataset in Pakistan Shah 2019 \cite{Shah2019FishPakFS}
\subsection{Automatic Metadata Generation}
Automatic metadata generation advances covering both descriptive and technical metadata are relevant to the research presented in this paper. Automatic metadata generation of descriptive bibliographic data has been a research focus for close to 20 years \cite{liddy2002automatic,greenberg2004metadata,cardinaels2005automating,paynter2005developing}. Researchers have applied support vector machine (SVM) approaches~\cite{han2003automatic}, and associated networks to address sparse and incomplete metadata~\cite{rodriguez2009automatic}, and various successes are integrated into day-to-day workflows. Heidorn, et al.~\cite{heidorn2008automatic} demonstrated the use of optical character recognition (OCR) to extract specimen information from the original typed and often hand-annotated labels that are digitized along with herbarium collection holdings. The extracted information was encoded in the DwC metadata associated with the specimen's digitized rendering. There has also been some success with extracting descriptive cartographic information from maps~\cite{manso2004automatic}. While descriptive metadata covers taxon, geographic location, and other important aspects, and may even record the image format; extensive use of automatic processes are still limited. More significantly, descriptive metadata does not not sufficiently addressed data quality.

Technical metadata, such as camera settings and temporal information (date and time) are automatically generated during a digitization sequence, following standards such as Exchangeable image file format (Exif)~\cite{Exif}. The camera's technical metadata that is automatically captured and inserted into digital image files at the time of capture. Some of this metadata may be useful when selecting a machine learning sample. A researcher may desire images with specific properties, such as being captured chiefly with a certain aperture setting. Even so, the majority of automatically captured technical metadata associated with digitized specimens is also insufficient for computational research, leaving researchers to rely on manually generated descriptive metadata, which itself is sparse and prone to human error. Fish image analysis research, as reviewed below, provides an opportunity to address current metadata shortcomings and needs specific to the selection of high-quality digitized specimen images for neural networks and the application of machine learning.

@@

Alsmadi et al.~\cite{Alsmadi2019RFE} implemented fish
classification through a meta-heuristic algorithm known as Memetic Algorithm (Genetic Algorithm with Simulated Annealing) with back-propagation algorithm (MA-B Classifier). They were able to classify 24 fish families with 90\%

@@

Especially in industrial settings it is necessary to automatically

@@

Another application of image analysis to fish images is the evaluation

@@

Digitized specimen accessible in open access repositories provide a rich,
extensive data source for machine-learning and scientific discovery.
These resources, however, remain largely untapped due to image quality
issues and metadata limitations.
The overall goal of our work addresses this need by combining
machine-learning and image informatics techniques to produce a computational
% . The overall goal of our research is to offer a machine-driven [*novel/innovative?? blah...]
alternative to the current manual metadata generation process, one that is
prohibitively costly in both terms of labor and time. Additionally, our
methods collectively provide a novel approach to computing higher-level
metadata that will support further scientific inquiry.

@@

Four key objectives are to:

@@

2) Investigate image processing at the pixel level.
Pilot testing found the detectron under-segmented the detected objects
with tightly enclosing bounding boxes. We will determine if
pixel analysis methods commonly found in image informatics may produce
more accurate bounding boxes and object masks.
% background as part of the fish, or the
% bounding box may clip away part(s) of the fish with
The specific aims of this objective are to:
%not sure we have to list all the details, but something like the below, with the 4 aspects of pixel analysis we tested/investigate/experimented with

\renewcommand{\labelenumi}{\alph{enumi}.}
\begin{enumerate}
\item
Identify the appropriate threshold value for more accurate mask.
% We will compute optimal scaling between [*or is it Otsu thresholding] to identify an improved threshold value. [Or we will determine is we can computed as the halfway point between the Otsu threshold value and the mean of the background intensities.]

@@

\item
Compute more accurate bounding box from updated mask.
% Adjusting the bounding box. [We will use computational methods for masking [calcuate a mask?] to determine if bounding box needs to be shrunk or expanded]
% Jane confused here, if this belongs here, or below

@@

The automated metadata generation methods for our project were developed to work on a specific set of images, the INHS\ Fish Collection~\cite{INHS}.  Most of these images have been configured, produced and acquired with a standard procedure.  The images used for our study contain one fish placed on a bright, white background and contain an information tag and the same ruler.  See Figure \ref{fig:INHS_examples} for three example images from the collection. While training and focusing our system on images with very similar compositions and visual properties may limit its immediate applicability, our efforts do demonstrate the potential that machine learning and image informatics techniques have for automatically generating metadata for biological specimen image collections.

>>>>

\section{Related Work}
\subsection{Metadata for Natural History Image Collection}
%question/comment - we need to keep in mind we are deal with digitized specimens, not simply digital, in other words, the artifacts themselves are digital version of physical, not like an x-ray, where the image is digital from the start.  
A number of different metadata standards have been applied to support the description and access of digitized scientific images. The Darwin Core (DwC)~\cite{biodiv_info_standards}, developed specifically to describe biological diversity data, is one of the most popular standards for such efforts. It is an extension of the Dublin Core's DCMI Metadata Terms~\cite{dc_terms}.
The Audubon Core~\cite{audub_core}, which supports the discoverability, dissemination, and use of data related to biological organisms (including 3--D digitized specimens), is a DwC extension that has become more popular. All of these descriptive standards and extensions include metadata properties for taxon, geographic location, and other important specimen content, and have been developed primarily from the perspective of a human curator. In other words, their application anticipates that a curator or data entry staff will manually generate metadata, drawn from acquisition logs or original specimen labels. This task is labor intensive, and the metadata associated with each digital rendering is generally sparse and more prone to human error, placing limitations on a researcher seeking to apply machine learning to the image and the metadata for scientific research.

This limitation is magnified when trying to assess the actual quality of the digitized specimen. Descriptive-oriented standards support search and retrieval, and the biodiversity community has advocated for data fitness standards \cite{chapman2020developing}. This point is also emphasized by
Wieczorek et al.~\cite{wieczorek2012darwin} in their report on the variety of DwC metadata extensions needed to meet growing community concerns and
requirements, including data quality and fitness. Even so, metadata describing image quality is severely limited and generally missing. This point is addressed in detail by Leipzig et al.~\cite{leipzig2021biodiversity} and serves as the rationale for Tulane University's effort to manually capture
content for 22 metadata properties that characterize digitized specimen image quality. Their work is being conducted in connection with the larger BGNN initiative, and the current process is costly in terms of labor and time, prone to human error and inconsistencies, and underscores the need to
explore automatic metadata generation methods.
%Fish species dataset in Pakistan Shah 2019 \cite{Shah2019FishPakFS}
\subsection{Automatic Metadata Generation}
Automatic metadata generation advances covering both descriptive and technical metadata are relevant to the research presented in this paper. Automatic metadata generation of descriptive bibliographic data has been a research focus for close to 20 years \cite{liddy2002automatic,greenberg2004metadata,cardinaels2005automating,paynter2005developing}. Researchers have applied support vector machine (SVM) approaches~\cite{han2003automatic}, and associated networks to address sparse and incomplete metadata~\cite{rodriguez2009automatic}, and various successes are integrated into day-to-day workflows. Heidorn, et al.~\cite{heidorn2008automatic} demonstrated the use of optical character recognition (OCR) to extract specimen information from the original typed and often hand-annotated labels that are digitized along with herbarium collection holdings. The extracted information was encoded in the DwC metadata associated with the specimen's digitized rendering. There has also been some success with extracting descriptive cartographic information from maps~\cite{manso2004automatic}. While descriptive metadata covers taxon, geographic location, and other important aspects, and may even record the image format; extensive use of automatic processes are still limited. More significantly, descriptive metadata does not sufficiently addressed data quality.

Technical metadata, such as camera settings and temporal information (date and time) are automatically generated during a digitization sequence, following standards such as Exchangeable image file format (Exif)~\cite{Exif}. The camera's technical metadata is automatically captured and inserted into digital image files at the time of acquisition. Some of this metadata may be useful when selecting a machine learning sample. A researcher may desire images with specific properties, such as being captured chiefly with a certain aperture setting. Even so, the majority of automatically registered technical metadata associated with digitized specimens is also insufficient for computational research, leaving researchers to rely on manually generated descriptive metadata, which itself is sparse and prone to human error.
Fish image analysis research, as reviewed below, demonstrates the
potential of automated computational methods to address current metadata shortcomings and needs specific to the selection of high-quality digitized specimen images for the application of machine learning.

@@

Alsmadi et al.~\cite{Alsmadi2019RFE} implemented fish classification
through a meta-heuristic algorithm known as the Memetic Algorithm.
% (Genetic Algorithm with Simulated Annealing) with back-propagation algorithm (MA-B Classifier).
They were able to classify 24 fish families with 90\% accuracy.

@@

Especially in industrial settings, it is necessary to automatically

@@

Another application of image analysis to fish images is the evaluation of

@@

Digitized specimens accessible in open-access repositories provide a rich,
extensive data source for machine learning and scientific discovery.
These resources, however, remain largely untapped due to image quality
issues and metadata limitations.
The overall goal of our work addresses this need by
% combining machine learning and image informatics techniques to produce
developing a computational
% . The overall goal of our research is to offer a machine-driven [*novel/innovative?? blah...]
alternative to the current manual metadata generation process, one that is
prohibitively costly in both terms of labor and time. Additionally, our
methods collectively provide a novel and general approach to computing
higher-level metadata that will support scientific inquiry based
on the analysis of specimen image collections.

@@

Our four key objectives are to:

@@

2) Investigate image processing at the pixel level.
Pilot testing found that \verb|detectron| under-segmented the detected objects
with tightly enclosing bounding boxes. We will determine if
pixel analysis methods commonly found in image informatics may produce
more accurate bounding boxes and object masks.
% background as part of the fish, or the
% bounding box may clip away part(s) of the fish with
The specific aims of this objective are to:
%not sure we have to list all the details, but something like the below, with the 4 aspects of pixel analysis we tested/investigate/experimented with

\renewcommand{\labelenumi}{\alph{enumi}.}
\begin{enumerate}
\item
Identify the appropriate threshold value for a more accurate mask.
% We will compute optimal scaling between [*or is it Otsu thresholding] to identify an improved threshold value. [Or we will determine is we can computed as the halfway point between the Otsu threshold value and the mean of the background intensities.]

@@

\item
Compute a more accurate bounding box from the updated mask.
% Adjusting the bounding box. [We will use computational methods for masking [calcuate a mask?] to determine if bounding box needs to be shrunk or expanded]
% Jane confused here, if this belongs here, or below

@@

The automated metadata generation methods for our project were developed to work on a specific set of images, the INHS\ Fish Collection~\cite{INHS}.  Most of these images have been configured, produced and acquired with a standard procedure.  The images used for our study contain one fish placed on a bright, white background and contain an information tag and the same ruler.  See Figure \ref{fig:INHS_examples} for three example images from the collection. While training and focusing our system on images with very similar compositions and visual properties may limit its immediate applicability, our efforts demonstrate the potential that machine learning and image informatics techniques have for automatically generating metadata for biological specimen image collections in general.
